Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-08-24 SolEnRevision_1/submission.tex
Created a revision directory

STPV, ST, and TPV systems all share common surfaces but operate under different conditions.  ST and STPV systems offer an alternative to PV power generation in alternative energy systems.  Since both are heat engines, they do not adhere to the Shockley-Queisser limit and can theoretically exhibit extremely high efficiencies.  Additionally, since both ST and STPV systems rely on elements heated to high temperatures via concentrated solar energy, they are easy to modify for thermal storage of energy~\cite{Night_time_Performance}.  This would allow them to operate into the night.  An advantage of ST systems over STPV systems is that ST systems do not require the use of PV cells.  The PV cells in STPV systems are expensive and can limit overall system size.  Conversely, an advantage of STPV systems over ST systems is that STPV systems have no thermal fluid or moving parts.  This leads to them being more stable and compact solutions.  Overall, ST tends to lend itself to large, immobile power installations while STPV is better suited for small applications.  TPV systems operate on the same principle as STPV systems, but rely on an external heat source instead of solar energy~\cite{Prototype_TPV}.  This allows them to be used in energy reclamation systems.

@@

In the case of STPV systems, the emitting 
surface will also play a role in device efficiency.  The ideal
surface will be a monochromatic emitter that emits radiation with energy equal to the 
bandgap energy of the PV cell used in the system~\cite{L_AIP_2007}.  Unfortunately, monochromatic 
emitters have a power density of 0, resulting in the requirement of an infinitely large 
emitting surface for practical power generation.  Therefore, in practical STPV systems, an 
emitting surface with a small bandwidth will be desirable~\cite{RF_OptExp_2009}.  
Figure~\ref{Ideal} 
shows the evolution of maximum system efficiency vs. temperature for an ideal system.
\begin{figure}[ht!]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} Maximum theoretical efficiency for various system temperatures.  Note the fast increase
around typical operation temperatures for ST and STPV systems.}
\end{center}
\end{figure}

@@

\subsection{Summary and outlook for theoretical design methodologies}
We have described a number of powerful theoretical methodologies that can be put to use to understand, predict, and even tailor the optical
response of systems of simple or complex nanostructures.  The use of these methods, along with the ingenuity of many researchers, has
allowed the design of many novel and useful systems for radiative control.  However, as will be discussed in more detail in the remaining sections, 
overall conversion efficiencies of TPV/STPV systems often fall around 3-8\%,  well short of the theoretical limit of 85\%.  A significant challenge remains in integrating
various theoretical methodologies to model and optimize global device performance~\cite{g4,g9}.
In principle, nanostructured systems may be designed or discovered by coupling the various electrodynamics modeling approaches described above 
to global optimization methods.  Generally, an appropriate figure-of-merit to be maximized is identified, e.g. the spectral efficiency which will
be discussed in detail later, and repeated calculations of the figure-of-merit are carried out while adjusting the features of the nanostructure until 
a global optimum is found.  A plethora of multi-parameter optimization methods are available and have been used in the context of optimizing the 
optical response of nanostructures, including clustering algorithms~\cite{g4}, the Simplex method~\cite{Simplex, CH_APL_2006}, genetic algorithms~\cite{ga,DB_JApplPhys_2007}, 
particle swarms~\cite{NDJ_JApplPhys_2012, ParticleSwarm}, and Gaussian
process modeling~\cite{miller1}.  Certainly one
challenge is that an integrated TPV/STPV system must couple together various optical modalities for absorption and emission.  Usually, this requires
abandoning exact analytical approaches in favor of approximate (e.g. perturbative) analytical approaches like coupled-mode theory.  Alternatively,
researchers must rely on the use of the numerical methodologies described above, 
though this may
prove daunting from a computational point of view due to the multi-scale nature of these systems.
Global system optimization must also include considerations like thermal management along with electrodynamics, as the
requisite operating temperatures can lead to oxidation or deformation of the
constituent structures and degradation of the device performance.  
Consideration of these various system parameters creates a highly heterogeneous optimization problem
and presents significant challenges for global optimization.  
However, several authors including Celanovic and co-workers~\cite{g4}
as well as Wang and co-workers~\cite{g9} have taken on the challenge of designing systems with optimal device consideration, which have led to device efficiencies approaching 3\% and 
10\%, respectively. Considering recent interest in exploiting near-field radiative heat-transfer to enhance
TPV/STPV power and conversion efficiency~\cite{SZF_NatNano_2016, KJ_SciRep_2016}, we anticipate that modeling methods that utilize
fluctuational electrodynamics~\cite{rodriguez2011,datas2013,didari2014,didari2015,edalatpour2014} will become increasingly important.
Similarly, appropriate modeling of radiative, electrical, and thermal loss mechanisms will be critical for helping to bridge
the gap between theory and experiment in the field~\cite{BDB_SciRep_2015}.

>>>>

STPV, ST, and TPV systems all share common surfaces but operate under different conditions.  ST and STPV systems offer an alternative to PV power generation in alternative energy systems.  Since both are heat engines, they do not adhere to the Shockley-Queisser limit and can theoretically exhibit extremely high efficiencies.  Additionally, since both ST and STPV systems rely on elements heated to high temperatures via concentrated solar energy, they are easy to modify for thermal storage of energy~\cite{SteadyStateAnalysis,Night_time_Performance}.  This would allow them to operate into the night.  An advantage of ST systems over STPV systems is that ST systems do not require the use of PV cells.  The PV cells in STPV systems are expensive and can limit overall system size.  Conversely, an advantage of STPV systems over ST systems is that STPV systems have no thermal fluid or moving parts.  This leads to them being more stable and compact solutions.  Overall, ST tends to lend itself to large, immobile power installations while STPV is better suited for small applications.  TPV systems operate on the same principle as STPV systems, but rely on an external heat source instead of solar energy~\cite{Prototype_TPV}.  This allows them to be used in energy reclamation systems.

@@

In the case of STPV systems, the emitting 
surface will also play a role in device efficiency.  The ideal
surface will be a monochromatic emitter that emits radiation with energy equal to the 
bandgap energy of the PV cell used in the system~\cite{TheoreticalEfficiency,L_AIP_2007}.  Unfortunately, monochromatic 
emitters have a power density of 0, resulting in the requirement of an infinitely large 
emitting surface for practical power generation.  Therefore, in practical STPV systems, an 
emitting surface with a small bandwidth will be desirable~\cite{RF_OptExp_2009}.  
Figure~\ref{Ideal} 
shows the evolution of maximum system efficiency vs. temperature for an ideal system.
\begin{figure}[ht!]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} Maximum theoretical efficiency for various system temperatures.  Note the fast increase
around typical operation temperatures for ST and STPV systems.}
\end{center}
\end{figure}

@@

\subsection{Summary and outlook for theoretical design methodologies}
We have described a number of powerful theoretical methodologies that can be put to use to understand, predict, and even tailor the optical
response of systems of simple or complex nanostructures.  The use of these methods, along with the ingenuity of many researchers, has
allowed the design of many novel and useful systems for radiative control.  However, as will be discussed in more detail in the remaining sections, 
overall conversion efficiencies of TPV/STPV systems often fall around 3-8\%,  well short of the theoretical limit of 85\%.  A significant challenge remains in integrating
various theoretical methodologies to model and optimize global device performance~\cite{g4,g9}.
In principle, nanostructured systems may be designed or discovered by coupling the various electrodynamics modeling approaches described above 
to global optimization methods.  Generally, an appropriate figure-of-merit to be maximized is identified, e.g. the spectral efficiency which will
be discussed in detail later, and repeated calculations of the figure-of-merit are carried out while adjusting the features of the nanostructure until 
a global optimum is found.  A plethora of multi-parameter optimization methods are available and have been used in the context of optimizing the 
optical response of nanostructures, including clustering algorithms~\cite{g4}, the Simplex method~\cite{Simplex, CH_APL_2006}, genetic algorithms~\cite{ga,DB_JApplPhys_2007}, 
particle swarms~\cite{NDJ_JApplPhys_2012, ParticleSwarm}, and Gaussian
process modeling~\cite{miller1}.  Certainly one
challenge is that an integrated TPV/STPV system must couple together various optical modalities for absorption and emission.  Usually, this requires
abandoning exact analytical approaches in favor of approximate (e.g. perturbative) analytical approaches like coupled-mode theory.  Alternatively,
researchers must rely on the use of the numerical methodologies described above, 
though this may
prove daunting from a computational point of view due to the multi-scale nature of these systems.
Global system optimization must also include considerations like thermal management along with electrodynamics, as the
requisite operating temperatures can lead to oxidation or deformation of the
constituent structures and degradation of the device performance.  
Consideration of these various system parameters creates a highly heterogeneous optimization problem
and presents significant challenges for global optimization.  
However, several authors including Celanovic and co-workers~\cite{g4}
as well as Wang and co-workers~\cite{g9} have taken on the challenge of designing systems with optimal device consideration, which have led to device efficiencies approaching 3\% and 
10\%, respectively. Considering recent interest in exploiting near-field radiative heat-transfer to enhance
TPV/STPV power and conversion efficiency~\cite{NearFieldConcentrated,SZF_NatNano_2016, KJ_SciRep_2016}, we anticipate that modeling methods that utilize
fluctuational electrodynamics~\cite{rodriguez2011,datas2013,didari2014,didari2015,edalatpour2014} will become increasingly important.
Similarly, appropriate modeling of radiative, electrical, and thermal loss mechanisms will be critical for helping to bridge
the gap between theory and experiment in the field~\cite{BDB_SciRep_2015}.
